The globular cluster system of the Auriga simulations

### 2019-08-19 AurigaGCS.tex
Semi-full rewrite of Sec. 4.3 to reflect updates to Figure 9 (which now shows a diverging colour map) for #1

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
mass in the MW (M31) GCS to obtain the median mass ratio produced by the star
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass ratio with respect to the MW (M31) GCS.

@@

We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
metallicities in the three innermost radial bins. In addition, Auriga produces 
fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for 
Auriga GCs within the Solar radius decreases with decreasing metallicity. This
means that either the formation efficiency should increase with decreasing metallicity,
or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GC system that can be similar to the GCS that is observed
in the Milky Way. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to Andromeda, the mass ratio (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
which suggests that both galaxies have diverse GC formation histories.
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GC system consistent with that of the Andromeda galaxy.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
we still find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
particles represent single stellar populations with a mass (resolution) consistent 
with that of GCs, they are in fact statistical tracers of the stellar population 
of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
may represent plausible formation sites of GCs, whereas the majority represents 
(halo) field stars - the disk component effectively falls outside our selection 
of star particles due to the age cut. It is implausible that all halo stars 
come from disrupted GCs because GC systems that survive down to redshift zero 
are generally few orders of magnitude less massive than galactic stellar haloes.

In general, the colour (metallicity) distribution of most GC systems is bimodal 
with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
1999AJ....118.1526G,2001AJ....121.2974L,2006ApJ...639...95P}. Indeed, 
\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} find that
the MW GCS has a bimodal [Fe/H] distribution: the latter fit a double Gaussian 
which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich) and 
dispersions of $0.34$ and $0.23$. Observations of GCs in M31, however, may be
best split into three distinct metallicity groups, one found at small radii with 
[Fe/H] $>-0.4$, one intermediate [Fe/H] group, and a dominant (metal-poor) group 
with [Fe/H] $< -1.5$ \citep{2016ApJ...824...42C}. The numerical simulation of
\citet{2017MNRAS.465.3622R} does yield a bimodal metallicity distribution where
the metal-poor population is dominated by accreted star particles and the metal-rich
population by {\it in~situ} stars.

We find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean
metallicity shifts when we split the GC candidates up according to birth location
(accreted or {\it in~situ}). In particular, the mean values of the old 
{\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
However, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. The Auriga simulations therefore do not support the view 
that the metal-poor GCs could have formed in satellites that have later been 
accreted whereas the metal-rich GC subpopulation has formed {\it in~situ}. With 
this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification appears flawed
in Au4-1.

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{the quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that gradual linear increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the Milky Way GCS.

>>>>

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc} (which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}). We notice that the Auriga simulations, 
on average, produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) 
than at higher metallicities in the three innermost radial bins. In addition, 
Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
and M31 GC systems.

To ease the comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such as scenario and
indicate a higher and lower than average mass excess. In particular, the median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the overall `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that mass excess for
Auriga GCs within the Solar radius decreases with decreasing metallicity. This
means that either the formation efficiency should increase with decreasing metallicity,
or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GC system that can be similar to the GCS that is observed
in the Milky Way. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to Andromeda, the mass ratio (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
which suggests that both galaxies have diverse GC formation histories.
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GC system consistent with that of the Andromeda galaxy.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity of GC candidates by 
$0.5$ dex with respect to all star particles, but we still find that the GC 
candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
Although the (old) star particles represent single stellar populations with a mass 
(resolution) consistent with that of GCs, they are in fact statistical tracers 
of the stellar population of the galaxy as a whole. Therefore only a (small) 
fraction of the star particles may represent plausible formation sites of GCs, 
whereas the majority represents (halo) field stars - the disk component effectively 
falls outside our selection of star particles due to the age cut. It is implausible 
that all halo stars come from disrupted GCs because the total mass in GC systems 
at redshift zero is generally a few orders of magnitude lower than the total 
mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
GCs, then the GC disruption rate would have to be considerably higher than expected
from theoretical models. Overall, our set of GC candidates most likely contains
an overabundance of regular stars. It could be that the resulting metallicity
distribution is then biased towards higher values than what is observed for real 
GCs. An alternative explanation could overmixing of metals at early times.

In general, the colour (metallicity) distribution of most GC systems is bimodal 
with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
1999AJ....118.1526G,2001AJ....121.2974L,2006ApJ...639...95P}. Indeed, 
\citet{1998gcs..book.....A} and \citet{Harris2001} find that the MW GCS has a 
bimodal [Fe/H] distribution. Observations of GCs in M31, however, may be best 
split into three distinct metallicity groups \citep{2016ApJ...824...42C}. The 
numerical simulation of \citet{2017MNRAS.465.3622R} does yield a bimodal 
metallicity distribution where the metal-poor population is dominated by accreted 
star particles and the metal-rich population by {\it in~situ} stars.

We find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GC systems at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
that the mean metallicity shifts when we split the GC candidates up according 
to birth location (accreted or {\it in~situ}). In particular, the mean values of 
the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
However, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. The Auriga simulations therefore do not support the view 
that the metal-poor GCs could have only formed in satellites that have later been 
accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification might not hold
for Au4-1.

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that a gradual increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the MW or M31 GCS.
